---
title: "EiA Prioritization"
author: "Peter Steward"
date: "1/4/2022"
output: html_document
runtime: shiny
---
  
<style type="text/css">
.main-container {
max-width: 1800px;
margin-left: auto;
margin-right: auto;
}
</style>

```{r setup, include=FALSE}
# Please run getwd() in the console to get the project location and copy into the line below
#root.dir<-"/Users/pstewarda/Library/CloudStorage/OneDrive-CGIAR/Projects/EiA/Climate Prioritization"
#knitr::opts_knit$set(root.dir = root.dir)
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
```

```{r Load packages,echo=F,message=F,warning=F}

if(!require("pacman", character.only = TRUE)){install.packages("pacman",dependencies = T)}

required.packages <- c("arrow",
                       "geoarrow",
                       "colourpicker",
                       "data.table",
                       "dplyr",
                       "DT",
                       "ggplot2",
                       "ggpubr",
                       "MetBrewer",
                       "miceadds",
                       "raster",
                       "reshape",
                       "shiny",
                       "terra",
                       "tidyverse",
                       "viridis",
                       "wesanderson",
                       "wbstats")

pacman::p_load(char=required.packages,install = T,character.only = T)

if(require("waffle")==F){
  devtools::install_github("hrbrmstr/waffle")
  require("waffle")
}
 
```

## EiA Spatial Prioritization  {.tabset .tabset-fade .tabset-pills}
```{r Palette,echo=F}

Viridis<-data.table(Source="viridis",Palette=c("magma","inferno","plasma","viridis","cividis","rocket","mako","turbo"))
Met<-data.table(Source="MetBrewer",Palette=names(MetBrewer::MetPalettes))
Wes<-data.table(Source="wesanderson",Palette=names(wesanderson::wes_palettes))

Palettes<-rbind(Viridis,Met)

PalFun<-function(PalName,N,Names) {
Viridis<-data.table(Source="viridis",Palette=c("magma","inferno","plasma","viridis","cividis","rocket","mako","turbo"))
Met<-data.table(Source="MetBrewer",Palette=names(MetBrewer::MetPalettes))
Palettes<-rbind(Viridis,Met)
    
 if(Palettes[Palette==PalName,Source]=="viridis"){
    PAL<-viridis::viridis(N,option=PalName)
 }

if(Palettes[Palette==PalName,Source]=="MetBrewer"){
     PAL<-MetBrewer::met.brewer(name=PalName, n=N, type="continuous")
}

  if(Palettes[Palette==PalName,Source]=="Wes"){
     PAL<-wesanderson::wes_palette(name=PalName, n=N, type="continuous")
  }
names(PAL)<-Names

return(PAL)
}
```

```{r load regions, echo=F}
region_file<-"Data/regions.geojson"
country_file<-"Data/countries.geojson"

cgiar_countries <- terra::vect(country_file)
cgiar_regions<-terra::vect(region_file)
```

```{r load hazards, echo =F}
# Load hazard layer 
hazard_file<-'Data/combi_haz_table_cg.asc/combi_haz_table_cg.asc'
Hazard<- terra::rast(hazard_file)
Hazard[Hazard$combi_haz_table_cg==0] <-NA
names(Hazard) <-'hazard'

HazTab<-data.table(Code=1:9,
                   Hazard=c('Drought (D)','Flood (F)','Climate variability (V)','D + V', 'Growing season reduction (R)', 'High growing season temperature (T)','F + T','V + T','Other combination'),
                   ShortName=c('D','F','V','D+V', 'R', 'T','F+T','V+T','Other'))
```

```{r load mapspam, echo =F}
spam_ssa_file_rs<-"Data/ssa_crop_vop15_intd15_rs.tif"
spam_global_file_rs<-"Data/global_crop_vop15_int15_rs.tif"

haz_vop_file<-"Data/hazard_vop_admin.parquet"

spam_africa<-terra::rast(spam_ssa_file_rs)
spam_global<-terra::rast(spam_global_file_rs)

# Read in summary of crop areas by region
SPAMbyRegion<-data.table::fread(file="Data/SPAMextracted.csv")[Country=="",Country:=NA]
```

```{r read hazard x exposure data v1 ,echo=F}
Data<-data.table(arrow::read_parquet(haz_vop_file))

# Add rank for plot 2
rank2<-unique(Data[order(VoP_total_crop,decreasing = T),.(VoP_total_crop,Region,Country,Crop)])[,Rank2:=1:.N]
Data<-merge(Data,rank2,by=c("Region","Crop","Country","VoP_total_crop"),all.x=T,sort=F)

# Set an mimimum VoP to consider
MinVoP<-10000 # $I 2015
Data<-Data[VoP>MinVoP]
SPAMbyRegion<-SPAMbyRegion[VoP>MinVoP]
```

```{r read hazards x exposure data v2, echo =F}
  Haz_Ext_File<-"Data/Haz_Ext.parquet"
  EX<-arrow::read_parquet(Haz_Ext_File)
```

```{r Create Plot Save Location,echo=F}
PlotDir<-"Plots"
if(!dir.exists(PlotDir)){
  dir.create(PlotDir)
}

```

### WafflePlot
```{r choose region, echo=F}
 cg_regions<- sort(unique(cgiar_regions$CG_REG))
 cg_regions_selected<-sort(unique(cgiar_countries$CG_REG))

  checkboxGroupInput(inputId="Regions", 
                     label="Select regions",
                     choices = cg_regions,
                     selected = cg_regions_selected,
                     inline=T)
```

```{r choose country, echo=F}
countries<-data.table(data.frame(cgiar_countries))

# Dynamically filter countries based on selected regions
renderUI({
  req(input$Regions) # Ensure regions are selected

  checkboxGroupInput(inputId="Countries", 
                   label="Select countries",
                   choices =    sort(countries[CG_REG %in% input$Regions|region %in% input$Regions,ADMIN]),
                   selected =NULL,
                   inline=T)
})
```

Select the number of crops for each region to show, the top n 

:::: {style="display: flex;"}
::: {}
```{r Choose N Crops, echo=F}
numericInput(inputId="Crop.N",
             label="No. of crops to show (plot1 - per country)",
             value=5,
             min=1,
             max=SPAMbyRegion[,list(N=length(unique(Crop))),by=Region][,max(N)],
             step=1,
             width="300px")
```
:::
:::{}
```{r Choose N Crops 2, echo=F}
numericInput(inputId="Crop.N2",
             label="No. of crops to show (plot2 - total)",
             value=20,
             min=1,
             max=50,
             step=1,
             width="300px")
```
:::
::::

Crops are present by region, the numbers refer to the regional rank of the crop in terms of the sum of the MapSPAM variable chosen for that crop (in this case value of production in 2015 international dollars I$).
```{r choose crops,echo=F}
renderUI({
  if(is.null(input$Countries)){
  checkboxGroupInput(inputId="Crops.Lab", 
                     label="Remove crop x region combinations",
                     choices = SPAMbyRegion[Region %in% input$Regions & Rank<=input$Crop.N & is.na(Country),Label],
                     selected = SPAMbyRegion[Region %in% input$Regions & Rank<=input$Crop.N & is.na(Country),Label],
                     inline=T)
  }else{
     checkboxGroupInput(inputId="Crops.Lab", 
                     label="Remove crop x country combinations",
                     choices = SPAMbyRegion[Region %in% input$Regions & Country %in% input$Countries & Rank<=input$Crop.N,Label],
                     selected = SPAMbyRegion[Region %in% input$Regions & Country %in% input$Countries & Rank<=input$Crop.N,Label],
                     inline=T) 
  }
})

```


```{r set default parameter values,echo=F}
Scaler<-200
NRows<-15
NRows2<-2
FacetRows<-1
TextSize<-20
TextWrap<-"No"
RmNoHaz<-"Yes"
LegPos<-"bottom"
PanelSpace<-0
GridSpace<-0.3
GridCols<-2
GridRows<-3
Palette<-"turbo"
Background<-"white"
GridCol<-"white"
NoHazardCol<-"grey50"
Plot.Height<-0.3
Plot.Width<-1.2


```

:::: {style="display: flex;"}
::: {}
```{r Scaling factor, echo=F}
numericInput(inputId="Scaler",
             label="Max blocks",
             value=Scaler,
             min=0,
             max=2000,
             step=50,
             width="100px")
```
:::
:::{}
```{r Number of Rows, echo=F}
numericInput(inputId="NRows",
             label="Waffle cols-plot1",
             value=NRows,
             min=1,
             max=30,
             step=1,
             width="120px")
```
:::
:::{}
```{r Number of Rows2, echo=F}
numericInput(inputId="NRows2",
             label="Waffle cols-plot2",
             value=NRows2,
             min=1,
             max=30,
             step=1,
             width="120px")
```
:::
:::{}
```{r Number of Facet Rows, echo=F}
numericInput(inputId="FacetRows",
             label="No. facet rows",
             value=FacetRows,
             min=1,
             max=30,
             step=1,
             width="120px")
```
:::
:::{}
```{r Text Size, echo=F}
numericInput(inputId="TextSize",
             label="Text Size",
             value=20,
             min=1,
             max=30,
             step=1,
             width="80px")
```
:::
:::{}
```{r Text Wrap, echo=F}
  selectInput(inputId="TextWrap", 
             label="Wrap labels?",
              choices = c("Yes","No"),
              selected=TextWrap, 
              multiple = F, 
              width="100px")
```
:::
:::{}
```{r RmNoHaz, echo=F}
  selectInput(inputId="RmNoHaz", 
             label="Remove No Hazard?",
              choices = c("Yes","No"),
              selected=RmNoHaz, 
              multiple = F, 
              width="140px")
```
:::
:::{}
```{r LegPos,echo=F}
  selectInput(inputId="LegPos", 
              label="Legend position",
              choices = c("bottom", "right", "top", "left"),
              selected=LegPos, 
              multiple = F, 
              width="120px")
```
:::
:::{}
```{r Facet spacing, echo=F}
numericInput(inputId="PanelSpace",
             label="Facet spacing",
             value=PanelSpace,
             min=1,
             max=30,
             step=1,
             width="110px")
```
:::
:::{}
```{r Grid spacing, echo=F}
numericInput(inputId="GridSpace",
             label="Grid spacing",
             value=GridSpace,
             min=0,
             max=3,
             step=0.01,
             width="110px")
```
:::
:::{}
```{r Grid Cols, echo=F}
numericInput(inputId="GridCols",
             label="Grid columns",
             value=GridCols,
             min=1,
             max=10,
             step=1,
             width="100px")
```
:::
:::{}
```{r Grid Rows, echo=F}

  numericInput(inputId="GridRows",
               label="Grid rows",
               value=GridRows,
               min=1,
               max=10,
               step=1,
               width="100px")

```
:::
::::

:::: {style="display: flex;"}
::: {}
```{r Choose Plot,echo=F}
  selectInput(inputId="plot_choice", 
              label="Choose plot",
              choices = c("plot1","plot2"),
              selected="plot1", 
              multiple = F, 
              width="120px")
```
:::
:::{}
```{r Choose Palette,echo=F}
  selectInput(inputId="Palette", 
              label="Palette",
              choices = Palettes[,sort(Palette)],
              selected=Palette, 
              multiple = F, 
              width="150px")

HazardPalette<-reactive({PalFun(PalName=input$Palette,
                      N=nrow(HazTab),
                      Names=HazTab$Hazard)
})
```
:::
:::{}
```{r Plot background colour picker, echo =F}
  colourInput(inputId="Background",
              label="Background colour",
              value=Background)
```
:::
:::{}
```{r Plot grid colour picker, echo =F}
  colourInput(inputId="GridCol",
              label="Grid colour",
              value=GridCol)
```
:::
:::{}
```{r Plot no hazard colour picker, echo =F}
  colourInput(inputId="NoHazardCol",
              label="No hazard colour",
              value=NoHazardCol)
```
:::
::::

:::: {style="display: flex;"}
::: {}
```{r BigP - Adjust Plot Height, echo=F}
numericInput(inputId="Plot.Height",
             label="Adjust plot height",
             value=Plot.Height,
             min=0.1,
             max=3,
             step=0.05, 
             width="200px")
```
:::
:::{}
```{r Adjust Plot Width , echo=F}
numericInput(inputId="Plot.Width",
             label="Adjust plot width",
             value=Plot.Width,
             min=0.1,
             max=3,
             step=0.1,
             width="200px")
```
:::
::::

```{r calculate units, echo=F}
square_val<-reactive({
  dat<-Data[Label %in% input$Crops.Lab]
  max_vop<-10^(nchar(dat[,max(VoP)])-2)
  dat[,VoP:=VoP/max_vop]
  scale_factor<-dat[,max(VoP,na.rm = T)/input$Scaler]
  round(scale_factor*max_vop/10^6,1)
})

square_val2<-reactive({
    if(is.null(input$Countries)){
    dat<-Data[Region %in% input$Regions & Country==""]
  }else{
    dat<-Data[Country %in% input$Countries]
  }
  ranks<-dat[,sort(unique(Rank2))]
  if(length(ranks)>input$Crop.N2){
  ranks<-ranks[1:input$Crop.N2]
    dat<-dat[Rank2 %in% ranks]
  } 
  max_vop<-10^(nchar(dat[,max(VoP)])-2)
  dat[,VoP:=VoP/max_vop]
  scale_factor<-dat[,max(VoP,na.rm = T)/input$Scaler]
  round(scale_factor*max_vop/10^6,1)
})

```

Plot 1: Waffle grid unit = `r reactive(square_val())` million IntD 2015. Plot 2: Waffle grid unit = `r reactive(square_val2())` million IntD 2015.

```{r create plot function, echo=F}
#https://rud.is/rpubs/building-waffle-charts.html 

Waffler<-function(data,
                  Crops.Lab,
                  Crop.N2,
                  Regions,
                  Countries,
                  Scaler,
                  NRows,
                  NRows2,
                  FacetRows,
                  TextSize,
                  HazardPalette,
                  LegPos,
                  PanelSpace,
                  TextWrap,
                  RmNoHaz,
                  Background,
                  NoHazardCol,
                  GridSpace,
                  GridCol){
  
  if(TextWrap=="Yes"){
    data[,Crops:=gsub("oil crops","oil-crops",Crops)]
    data[!grepl(" ",Crop),Crop:=paste0(Crop,"\n")]
    data[,Crop:=gsub(" ","\n",Crop)]
  }

  if(RmNoHaz=="Yes"){
    data<-data[Hazard!="No hazard"]
  }
  
   if(RmNoHaz=="No"){
    HazardPalette[names(HazardPalette)=="No Hazard"]<-NoHazardCol
  }
  
  # Create combined names
  data[, Combined := paste0(Admin, ":", Crop)]
  data[, Combined := factor(Combined, levels = data[, .(Total = sum(VoP)), by = Combined][order(-Total), Combined])]
  
  # Factorize hazard
  data[,Hazard:=factor(Hazard,levels=sort(unique(Hazard)))]

  # Data for plot 1
  data1<-data[Label %in% Crops.Lab]
  max_vop<-10^(nchar(data1[,max(VoP)])-2)
  data1[,VoP:=VoP/max_vop]
  scale_factor<-data1[,max(VoP,na.rm = T)/Scaler]
  data1[,VoP:=round(VoP/scale_factor,0)]
  MaxY<-data1[,list(Height=ceiling(sum(VoP)/NRows)),by=.(Region,Country,Crop)][,max(Height)]+1
  data1<-data1[VoP>0]
  
  # Data for plot 2
  if(is.null(Countries)){
    data2<-data[Region %in% Regions & Country==""]
  }else{
    data2<-data[Country %in% Countries]
  }
  ranks<-data2[,sort(unique(Rank2))]
  if(length(ranks)>Crop.N2){
  ranks<-ranks[1:Crop.N2]
  data2<-data2[Rank2 %in% ranks]
  }
  max_vop<-10^(nchar(data2[,max(VoP)])-2)
  data2[,VoP:=VoP/max_vop]
  scale_factor<-data2[,max(VoP,na.rm = T)/Scaler]
  data2[,VoP:=round(VoP/scale_factor,0)]
  data2<-data2[VoP>0]

  # Plot 2
gg_theme <- theme(
  text = element_text(size = TextSize),
  plot.margin = margin(0, 0, 0, 0, unit = "cm"), # Remove plot margin
  panel.spacing = unit(0, "lines"), # No space between panels
  axis.ticks = element_blank(),
  axis.line = element_blank(),
  panel.background = element_rect(fill = Background),
  strip.background = element_blank(),
  strip.text.y.left = element_text(
    angle = 0,                # Horizontal strip labels
    hjust = 1,                # Align strip labels horizontally
    vjust = 0.5,              # Center vertically
    margin = margin(r = 0, l = 0, unit = "pt") # Remove strip margins
  ),
  axis.text = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank()
)

  g <- ggplot(data2, aes(fill = Hazard, values = VoP)) +
  waffle::geom_waffle(n_rows = NRows2, size = GridSpace, colour = GridCol, flip = FALSE) +
  scale_fill_manual(values = HazardPalette, drop = FALSE) +
  scale_x_continuous(expand = c(0.005,0))+
  scale_y_continuous(expand = c(0.02,0.02))+
  facet_grid(Combined ~ ., switch = "y") + # Use facet_grid with switched strips
  gg_theme

  # Plot 1
  gg_theme<-theme(text=element_text(size=TextSize),
          panel.spacing = unit(PanelSpace,"lines"),
          axis.ticks = element_blank(),
          axis.line = element_blank(),
          panel.background = element_rect(fill=Background),
          strip.background = element_blank(),
          strip.text = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")),
          plot.margin = margin(0, 0, 0, 0, unit = "cm"), 
          axis.text = element_blank(),
          axis.title = element_blank(),
          panel.grid = element_blank()
          )
  
  admin<-data1[,sort(unique(Admin))]
  Plots<-lapply(admin,FUN=function(REG){
    
    Plot.Dat<-data1[Admin==REG]
    
    Plot.Dat[,Crop:=factor(Crop,levels = unique(Plot.Dat[,.(Crop,Rank)])[order(as.numeric(Rank)),Crop])]
  
  g<-ggplot(Plot.Dat,aes(fill = Hazard, values = VoP)) +
    expand_limits(x=c(0,0), y=c(0,0)) +
    coord_equal() +
    labs(fill = NULL, colour = NULL) +
    waffle::geom_waffle(n_rows = NRows, size = GridSpace, colour = GridCol, flip = TRUE)+
    gg_theme+
    scale_fill_manual(values=HazardPalette,drop=F)+
    facet_wrap(~Crop, nrow = FacetRows, strip.position = "bottom")+
    scale_y_continuous(limits=c(0,MaxY),expand = c(0,0))
  
  g

  })
  
  names(Plots)<-admin

  return(list(Plot1=Plots,Plot2=g))
}

```

```{r create plots,echo=F}
PlotData<-reactive({
  Waffler(data=copy(Data),
          Crops.Lab=input$Crops.Lab,
          Crop.N2=input$Crop.N2,
          Regions=input$Regions,
          Countries=input$Countries,
          Scaler=input$Scaler,
          NRows=input$NRows,
          NRows2=input$NRows2,
          FacetRows=input$FacetRows,
          TextSize=input$TextSize,
          HazardPalette=HazardPalette(),
          LegPos=input$LegPos,
          PanelSpace=input$PanelSpace,
          TextWrap=input$TextWrap,
          RmNoHaz=input$RmNoHaz,
          Background=input$Background,
          NoHazardCol=input$NoHazardCol,
          GridSpace=input$GridSpace,
          GridCol=input$GridCol)
})

```

```{r Plot Size Adjust Functions , echo=F}
Plot.Height <- function(){
  x<-  input$Plot.Height*400*length(PlotData()$Plot1)
  if(input$plot_choice=="plot2"){
  x<- input$Plot.Height*(50+input$Crop.N2*100)
  }
  return(x)
}

Plot.Width <- function(){
  input$Plot.Width*1200
}
```

```{r Plot waffles,echo=F}
renderPlot({
  if(input$plot_choice=="plot1"){
  ggpubr::ggarrange(plotlist=PlotData()$Plot1, 
                    ncol=input$GridCols,
                    nrow=input$GridRows, 
                    common.legend = TRUE, 
                    legend=input$LegPos)
  }else{
     PlotData()$Plot2
  }
  },height= Plot.Height,width=Plot.Width)
```


:::: {style="display: flex;"}
::: {}
```{r  Save Waffle Option, echo=F}
selectInput(inputId="Waffle.Save.Plot", 
            label="Enable Save?",
            choices = c("Yes","No"),
            selected="No",
            width="150px")   
```
:::
:::{}
```{r Waffle Save Width, echo=F}
numericInput(inputId="Waffle.Width",
             label="Plot save width (mm)", 
             value=180,
             min=30,
             max=300,
             step=10,
             width="200px")  
```         
:::
:::{}
```{r Waffle Save Height, echo=F}
numericInput(inputId="Waffle.Height",
             label="Plot save height (mm)", 
             value=180,
             min=30,
             max=300,
             step=10,
             width="220px")  
```   
:::
:::{}
```{r Waffle Scale Height, echo=F}
numericInput(inputId="Waffle.Scale",
             label="Plot scaling", 
             value=1.8,
             min=0.5,
             max=4,
             step=0.1,
             width="200px")  
``` 
:::
:::{}
```{r Waffle - Plot Filename, echo=F}
textInput(inputId="Waffle.Filename",
          label="Enter Waffle filename", 
          value="Waffle")

```
:::
::::
  
```{r Save Waffle, echo=F}
reactive({
  if(input$Waffle.Save.Plot=="Yes"){
    ggsave(filename = paste0(input$Waffle.Filename,".png"),
           plot =   ggpubr::ggarrange(plotlist=PlotData(), 
                    ncol=input$GridCols,
                    nrow=input$GridRows, 
                    common.legend = TRUE, 
                    legend=input$LegPos),
           path = PlotDir,
           width= input$Waffle.Width,
           height = input$Waffle.Height,
           units = "mm",
           scale = input$Waffle.Scale,
           dpi = 600,
           type = "cairo")
  }
})
```


#### Data used the waffle plot:
```{r Show Data,echo=F}
renderDT({
  datatable(Data[,!c("Admin","Label","Rank","Rank2")][,Unit:=paste("2015",input$Units)],
            caption="Plot data by crop x region x hazard",
            extensions = 'Buttons',
            filter = "top",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),c(10,25,50,"All"))))
  
})
```

### Hazard map
:::: {style="display: flex;"}
::: {}
```{r select hazard map country,echo=F}
selectInput(
  inputId = "SelectedCountry",
  label = "Select a Country:",
  choices = c("All", sort(unique(cgiar_countries$ADMIN))),
  selected = "All",
  multiple = T,
  width = "200px"
)
```
:::
:::{}
```{r Adjust Map Height, echo=F}
numericInput(inputId="Map.Height",
             label="Adjust map height",
             value=1,
             min=0.1,
             max=3,
             step=0.1, 
             width="160px")
```
:::
:::{}
```{r Adjust Map Width , echo=F}
numericInput(inputId="Map.Width",
             label="Adjust map width",
             value=1,
             min=0.1,
             max=3,
             step=0.1,
             width="160px")
```
:::
:::{}
```{r Map border colour picker, echo =F}
  colourInput(inputId="MapBorder",
              label="Border colour",
              value="black")
```
:::
:::{}
```{r Border Width , echo=F}
numericInput(inputId="BorderWidth",
             label="Border width",
             value=0.2,
             min=0.1,
             max=2,
             step=0.1,
             width="120px")
```
:::
:::{}
```{r Map Text Size , echo=F}
numericInput(inputId="MapTextSize",
             label="Text size",
             value=16,
             min=1,
             max=30,
             step=1,
             width="120px")
```
:::
::::

```{r Create Hazard Map Function,echo=F}

WorldMapFun<-function(PalName,
                      Hazard,
                      cgiar_countries,
                      SelectedCountry,
                      MapBorder,
                      BorderWidth,
                      TextSize,
                      HazTab){
  
HazardPalette<-PalFun(PalName=PalName,
                      N=nrow(HazTab),
                      Names=HazTab$ShortName)

Hazards_Plot<-data.table(as.data.frame(raster::crop(raster::mask(Hazard,cgiar_countries),cgiar_countries),xy=T))
setnames(Hazards_Plot,"hazard","Code")
Hazards_Plot<-merge(Hazards_Plot,HazTab[,list(Code,ShortName)],by="Code",all.x=T)
setnames(Hazards_Plot,"ShortName","Hazards")

world <- ggplot2::map_data("world")

if(SelectedCountry!="All"){
  cgiar_countries<-cgiar_countries[cgiar_countries$ADMIN %in% SelectedCountry,]
}

Countries<-cgiar_countries$ADMIN
Countries[Countries=="The Bahamas"]<-"Bahamas"
Countries[Countries=="Republic of the Congo"]<-"Republic of Congo"
Countries[Countries=="Guinea Bissau"]<-"Guinea-Bissau"
Countries[Countries=="East Timor"]<-"Timor-Leste"
Countries[Countries=="Trinidad and Tobago"]<-"Trinidad"
Countries[Countries=="United Republic of Tanzania"]<-"Tanzania"
Countries[Countries=="Saint Vincent and the Grenadines"]<-"Saint Vincent"
Countries[Countries=="eSwatini"]<-"Swaziland"
Countries[Countries=="United States Virgin Islands"]<-"Virgin Islands"
Countries<-Countries[!Countries %in% c("Netherlands","France")]

Hazards_Plot<-terra::crop(Hazards_Plot,cgiar_countries)


world<-world[world$region %in% Countries,]

g <- ggplot() +
  geom_tile(
    data = Hazards_Plot,
    aes(x = x, y = y, fill = Hazards)
  ) +
  scale_fill_manual(values = HazardPalette, na.value = "white") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  geom_map(
    data = world,
    map = world,
    aes(map_id = region),
    color = MapBorder, 
    fill = NA, 
    linewidth = BorderWidth
  ) +
  coord_quickmap() +
  theme(
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    text = element_text(size = TextSize, face = "bold"),
    legend.position = c(0.8, 0.2),
    plot.background = element_blank(),
    panel.background = element_blank()
  ) +
  guides(fill = guide_legend(ncol = 2))


return(g)
}
```

```{r create plot,echo=F}
Map<-reactive({
  WorldMapFun(PalName=input$Palette,
              Hazard = Hazard,
              cgiar_countries = cgiar_countries,
              SelectedCountry=input$SelectedCountry,
              MapBorder=input$MapBorder,
              BorderWidth=input$BorderWidth,
              TextSize = input$MapTextSize,
              HazTab = HazTab)
  })
```


```{r Map Size Adjust Functions , echo=F}
Map.Height <- function(){
  input$Map.Height*442
}

Map.Width <- function(){
  input$Map.Width*1200
}
```


```{r Plot Hazard Map,echo=F}
renderPlot({Map()},height=Map.Height,width=Map.Width)
```


:::: {style="display: flex;"}
::: {}
```{r  Save Map, echo=F}
selectInput(inputId="Map.Save.Plot", 
            label="Enable Save?",
            choices = c("Yes","No"),
            selected="No",
            width="120px")   
```
:::
:::{}
```{r Map Save Width, echo=F}
numericInput(inputId="Map.Save.Width",
             label="Map save width (mm)", 
             value=180,
             min=30,
             max=300,
             step=10,
             width="170px")  
```         
:::
:::{}
```{r Map Save Height, echo=F}
numericInput(inputId="Map.Save.Height",
             label="Map save height (mm)", 
             value=round(180*0.37),
             min=30,
             max=300,
             step=10,
             width="200px")  
```   
:::
:::{}
```{r Map Scale Height, echo=F}
numericInput(inputId="Map.Scale",
             label="Text scaling", 
             value=1.5,
             min=0.5,
             max=4,
             step=0.1,
             width="100px")  
``` 
:::
:::{}
```{r Map - Plot Filename, echo=F}
textInput(inputId="Map.Filename",
          label="Enter map filename", 
          value="Map")

```
:::
::::
  
```{r Save map, echo=F}

reactive({
  if(input$Map.Save.Plot=="Yes"){
    ggsave(filename = paste0(input$Map.Filename,".png"),
           plot = Map(),
           path = PlotDir,
           width= input$Map.Save.Width,
           height = input$Map.Save.Height,
           units = "mm",
           scale = input$Map.Scale,
           dpi = 600,
           type = "cairo")
  }
})



```

### Country x Hazard Table
```{r extract country data,echo=F}
renderDT({
  datatable(EX,
            caption="Cropland Hazards by Country",
            extensions = 'Buttons',
            colnames = c('Country', 'Crop area (km2)', '% crop at risk', 'Rural pop (M)',   '% pop at risk','Pop at risk (M)',colnames(EX)[7:length(colnames(EX))]), 
            filter = "top",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),c(10,25,50,"All"))))
  
})

```