---
title: "EiA Prioritization"
author: "Peter Steward"
date: "1/4/2022"
output: html_document
runtime: shiny
---
  
<style type="text/css">
.main-container {
max-width: 1800px;
margin-left: auto;
margin-right: auto;
}
</style>

```{r setup, include=FALSE}
# Please run getwd() in the console to get the project location and copy into the line below
#root.dir<-"/Users/pstewarda/Library/CloudStorage/OneDrive-CGIAR/Projects/EiA/Climate Prioritization"
#knitr::opts_knit$set(root.dir = root.dir)
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
```

```{r Load packages,echo=F,message=F,warning=F}

if(!require("pacman", character.only = TRUE)){install.packages("pacman",dependencies = T)}

required.packages <- c("arrow",
                       "geoarrow",
                       "colourpicker",
                       "data.table",
                       "dplyr",
                       "DT",
                       "ggplot2",
                       "ggpubr",
                       "MetBrewer",
                       "miceadds",
                       "raster",
                       "reshape",
                       "shiny",
                       "terra",
                       "tidyverse",
                       "viridis",
                       "wesanderson")

pacman::p_load(char=required.packages,install = T,character.only = T)

if(require("waffle")==F){
  devtools::install_github("hrbrmstr/waffle")
  require("waffle")
}
 
```

## EiA Spatial Prioritization  {.tabset .tabset-fade .tabset-pills}
```{r Palette,echo=F}

Viridis<-data.table(Source="viridis",Palette=c("magma","inferno","plasma","viridis","cividis","rocket","mako","turbo"))
Met<-data.table(Source="MetBrewer",Palette=names(MetBrewer::MetPalettes))
Wes<-data.table(Source="wesanderson",Palette=names(wesanderson::wes_palettes))

Palettes<-rbind(Viridis,Met)

PalFun<-function(PalName,N,Names) {
Viridis<-data.table(Source="viridis",Palette=c("magma","inferno","plasma","viridis","cividis","rocket","mako","turbo"))
Met<-data.table(Source="MetBrewer",Palette=names(MetBrewer::MetPalettes))
Palettes<-rbind(Viridis,Met)
    
 if(Palettes[Palette==PalName,Source]=="viridis"){
    PAL<-viridis::viridis(N,option=PalName)
 }

if(Palettes[Palette==PalName,Source]=="MetBrewer"){
     PAL<-MetBrewer::met.brewer(name=PalName, n=N, type="continuous")
}

  if(Palettes[Palette==PalName,Source]=="Wes"){
     PAL<-wesanderson::wes_palette(name=PalName, n=N, type="continuous")
  }
names(PAL)<-Names

return(PAL)
}
```

### Load and prepare data
```{r load regions}
# CGIAR regions
cgiar_countries <- terra::vect('Data/CGIAR_countries_simplified.geojson')
cgiar_regions<-terra::aggregate(cgiar_countries,by="CG_REG")
```

```{r load hazards}
# Load hazard layer 
hazard_file<-'Data/combi_haz_table_cg.asc/combi_haz_table_cg.asc'
Hazard<- terra::rast(hazard_file)
Hazard[Hazard$combi_haz_table_cg==0] <-NA
names(Hazard) <-'hazard'

HazTab<-data.table(Code=1:9,
                   Hazard=c('Drought (D)','Flood (F)','Climate variability (V)','D + V', 'Growing season reduction (R)', 'High growing season temperature (T)','F + T','V + T','Other combination'),
                   ShortName=c('D','F','V','D+V', 'R', 'T','F+T','V+T','Other'))
```

Cropland extent data comes from https://glad.umd.edu/dataset/croplands
```{r load global crop land extent}
Haz_Ext_File<-"Data/Haz_Ext.parquet"

if(!file.exists(Haz_Ext_File)){
Cropland<-terra::rast("Data/Global_cropland_3km_2019.tif")

HazardCrop<-terra::rast(hazard_file)
crs(HazardCrop)<-crs(Cropland)

# Resample to hazard layer
Cropland<-terra::resample(Cropland,HazardCrop)

# Convert % to km2
CroplandSize<-terra::cellSize(Cropland,unit="km")
Cropland<-(Cropland/100)*CroplandSize
}

```

```{r load mapspam}
spam_ssa_file<-"Data/SPAM/ssa_crop_vop15_intd15.tif"
spam_global_file<-"Data/SPAM/global_crop_vop15_int15.tif"

spam_ssa_file_rs<-gsub(".tif$","_rs.tif",spam_ssa_file)
spam_global_file_rs<-gsub(".tif$","_rs.tif",spam_global_file)

haz_vop_file<-"Data/hazard_vop_admin.parquet"

if(!file.exists(spam_ssa_file_rs)){
  Cropland<-terra::rast("Data/Global_cropland_3km_2019.tif")
  
  HazardCrop<-terra::rast(hazard_file)
  crs(HazardCrop)<-crs(Cropland)
  
  spam_africa<-terra::rast(spam_ssa_file)
  spam_global<-terra::rast(spam_global_file)
  
  # Resmaple to hazards
  cs<-cellSize(spam_africa,unit="km")
  spam_africa_d<-spam_africa/cs
  spam_africa_d<-terra::resample(spam_africa_d,Hazard)
  spam_africa<-spam_africa_d*cellSize(spam_africa_d,unit="km")
  
  terra::writeRaster(spam_africa,filename=spam_ssa_file_rs)
  
  # Resmaple to hazards
  cs<-cellSize(spam_global,unit="km")
  spam_global_d<-spam_global/cs
  spam_global_d<-terra::resample(spam_global_d,Hazard)
  spam_global<-spam_global_d*cellSize(spam_global_d,unit="km")
  
  terra::writeRaster(spam_global,filename=spam_global_file_rs,overwrite=T)

}else{
  if(!file.exists(haz_vop_file)){
  spam_africa<-terra::rast(spam_ssa_file_rs)
  spam_global<-terra::rast(spam_global_file_rs)
  }
}

# Run R/SPAMbyRegion.R to generate the file below
# Read in summary of crop areas by region, remove crops with small areas
SPAMbyRegion<-data.table::fread(file="Data/SPAMextracted.csv")[Country=="",Country:=NA]
```

```{r extract hazard x vop by admin area ,echo=F}

if(!file.exists(haz_vop_file)){
  RegxCrop<-rbindlist(lapply(strsplit(SPAMbyRegion$Label,"-"),FUN=function(X){data.table(Region=X[1],Country=X[2],Crop=X[3],Rank=X[4])}))
  areas<-unique(RegxCrop[,.(Region,Country)])
  
  Data<-rbindlist(pbapply::pblapply(1:nrow(areas),FUN=function(i){
    REG<-areas$Region[i]
    country<-areas$Country[i]
  
    Crops<-RegxCrop[Region==REG & Country==country,as.character(Crop)]
    # Load crops for selected region
    if(REG %in% c("ESA","WCA")){
     SPAM<-spam_africa
    }else{
      SPAM<-spam_global
    }
    
    # Hazard descriptions table
    HazTab<-data.table(Code=1:9,Hazard=c('Drought (D)','Flood (F)','Climate variability (V)','D + V', 'Growing season reduction (R)', 'High growing season temperature (T)','F + T','V + T','Other combination'))
    
    # Crop & hazard by selected CGIAR region
    if(country!=""){
      Region<-cgiar_countries[cgiar_countries$CG_REG==REG & cgiar_countries$ADMIN==country,]
    }else{
      Region<-cgiar_regions[cgiar_regions$CG_REG==REG,]
    }
    
    SPAM <- terra::mask(terra::crop(SPAM,Region),Region)
    Haz<-terra::mask(terra::crop(Hazard,Region),Region)

    dff<-rbindlist(lapply(1:nlyr(SPAM),FUN=function(i){
      # Take one crop
      cr1 <- SPAM[[i]]

      ex<-data.table(VoP=as.numeric(values(cr1)),Code=as.numeric(values(Haz)))
      ex<-merge(ex,HazTab,by="Code",all.x=T)
      ex<-ex[,list(VoP=sum(VoP,na.rm = T)),by=list(Hazard)
             ][,Crop:=names(cr1)]
            ex
    }))
    
    dff[,Region:=REG][,Country:=country]
    
    dff
  }))
  
  Data<-merge(Data,RegxCrop,by=c("Region","Country","Crop"),all.x=T,sort=F)
  Data[,VoP_total_crop:=sum(VoP,na.rm=T),by=.(Region,Country,Crop)
       ][,VoP_total:=sum(VoP,na.rm=T),by=.(Region,Country)
         ][,VoP_perc_total:=round(100*VoP/VoP_total,2)
           ][,Label:=paste0(Region,"-",Country,"-",Crop,"-",Rank)
             ][,VoP:=round(VoP,0)
               ][,VoP_total_crop:=round(VoP_total_crop,0)
                 ][,VoP_perc_total:=round(VoP_perc_total,0)]
  
  
  Data[is.na(Hazard),Hazard:="No hazard"]
  
  # Remove rows with zero value
  Data<-Data[VoP>0]
  # Add back label
  Data[,Label:=paste0(Region,"-",Country,"-",Crop,"-",Rank)][,Admin:=Country][Admin=="",Admin:=Region]

  arrow::write_parquet(Data,haz_vop_file)
  
}else{
  Data<-data.table(arrow::read_parquet(haz_vop_file))
}

# Add rank for plot 2
rank2<-unique(Data[order(VoP_total_crop,decreasing = T),.(VoP_total_crop,Region,Country,Crop)])[,Rank2:=1:.N]
Data<-merge(Data,rank2,by=c("Region","Crop","Country","VoP_total_crop"),all.x=T,sort=F)

# Set an mimimum VoP to consider
MinVoP<-10000 # $I 2015
Data<-Data[VoP>MinVoP]
SPAMbyRegion<-SPAMbyRegion[VoP>MinVoP]
```

```{r load population}
if(!file.exists(Haz_Ext_File)){
   HazardCrop<-terra::rast(hazard_file)
    crs(HazardCrop)<-crs(Cropland)
  
  
  Population<-terra::rast("Data/cell5m_ruralpop_2020_v3.tif")
  TotalPop<-terra::resample(terra::crop(Population,HazardCrop),HazardCrop)
  names(TotalPop)<-"TotalPop"
  MaskedPop<-terra::mask(TotalPop,HazardCrop)
  names(MaskedPop)<-"AtRiskPop"
}
```

Extract cropland hazards by country
```{r extract country level data}
if(!file.exists(Haz_Ext_File)){
  
  HazardCrop<-terra::rast(hazard_file)
  crs(HazardCrop)<-crs(Cropland)
  
  EX<-data.table(terra::extract(c(HazardCrop,Cropland,TotalPop,MaskedPop),cgiar_countries))
  
  EX<-merge(EX,data.table(ID=1:length(cgiar_countries),Country=cgiar_countries$ADMIN),by="ID",all.x=T)
  
  # Hazard descriptions table
  setnames(EX,"combi_haz_table_cg","Code")
  
  EX<-merge(EX,HazTab[,list(Code,ShortName)],by="Code",all.x=T)[,ID:=NULL][,Code:=NULL]
  setnames(EX,"ShortName","Hazard")
  
  EX[is.na(Hazard),Hazard:="No Hazard"]
  
  EX<-EX[,list(Cropland.Area=round(sum(Global_cropland_3km_2019)),
               RuralPop=round(sum(TotalPop,na.rm=T)),
               RuralPopRisk=round(sum(AtRiskPop,na.rm = T))),by=list(Country,Hazard)
         ][,Total.Area:=sum(Cropland.Area),by=Country
         ][,RuralPop:=sum(RuralPop),by=Country
         ][,RuralPopRisk:=sum(RuralPopRisk),by=Country
           ][,Cropland.Perc:=round(100*Cropland.Area/Total.Area,1)
             ][!is.na(Hazard)
               ][,Cropland.Area:=NULL
                 ][,Total.Perc:=sum(Cropland.Perc),by=Country
                   ][,RuralPopRiskPerc:=round(100*RuralPopRisk/RuralPop,1)
                     ][,RuralPop:=round(RuralPop/10^6,1)
                       ][,RuralPopRisk:=round(RuralPopRisk/10^6,1)]
  
  EX<-dcast(EX,Country+Total.Area+Total.Perc+RuralPop+RuralPopRiskPerc+RuralPopRisk~Hazard,value.var = "Cropland.Perc")[Total.Area!=0]

  arrow::write_parquet(EX,Haz_Ext_File)
}else{
  EX<-arrow::read_parquet(Haz_Ext_File)
}


```

```{r Create Plot Save Location,echo=F}
PlotDir<-"Plots"
if(!dir.exists(PlotDir)){
  dir.create(PlotDir)
}

```

### WafflePlot
```{r choose region, echo=F}
  checkboxGroupInput(inputId="Regions", 
                     label="Select regions",
                     choices = sort(unique(cgiar_countries$CG_REG)),
                     selected = sort(unique(cgiar_countries$CG_REG)),
                     inline=T)
```

```{r choose country, echo=F}
countries<-data.table(data.frame(cgiar_countries))

# Dynamically filter countries based on selected regions
renderUI({
  req(input$Regions) # Ensure regions are selected

  checkboxGroupInput(inputId="Countries", 
                   label="Select countries",
                   choices =    sort(countries[CG_REG %in% input$Regions,ADMIN]),
                   selected =NULL,
                   inline=T)
})
```

Select the number of crops for each region to show, the top n 
```{r Choose N Crops, echo=F}
numericInput(inputId="Crop.N",
             label="No. of crops to show (plot1 - per country)",
             value=5,
             min=1,
             max=SPAMbyRegion[,list(N=length(unique(Crop))),by=Region][,max(N)],
             step=1,
             width="300px")
```

```{r Choose N Crops 2, echo=F}
numericInput(inputId="Crop.N2",
             label="No. of crops to show (plot2 - total)",
             value=20,
             min=1,
             max=50,
             step=1,
             width="300px")
```

Crops are present by region, the numbers refer to the regional rank of the crop in terms of the sum of the MapSPAM variable chosen for that crop (in this case value of production in 2015 international dollars I$).
```{r choose crops,echo=F}
renderUI({
  if(is.null(input$Countries)){
  checkboxGroupInput(inputId="Crops.Lab", 
                     label="Remove crop x region combinations",
                     choices = SPAMbyRegion[Region %in% input$Regions & Rank<=input$Crop.N & is.na(Country),Label],
                     selected = SPAMbyRegion[Region %in% input$Regions & Rank<=input$Crop.N & is.na(Country),Label],
                     inline=T)
  }else{
     checkboxGroupInput(inputId="Crops.Lab", 
                     label="Remove crop x country combinations",
                     choices = SPAMbyRegion[Region %in% input$Regions & Country %in% input$Countries & Rank<=input$Crop.N,Label],
                     selected = SPAMbyRegion[Region %in% input$Regions & Country %in% input$Countries & Rank<=input$Crop.N,Label],
                     inline=T) 
  }
})

```

:::: {style="display: flex;"}
::: {}
```{r Scaling factor, echo=F}
numericInput(inputId="Scaler",
             label="Max blocks",
             value=200,
             min=0,
             max=2000,
             step=50,
             width="100px")
```
:::
:::{}
```{r Number of Rows, echo=F}
numericInput(inputId="NRows",
             label="Waffle cols-plot1",
             value=15,
             min=1,
             max=30,
             step=1,
             width="120px")
```
:::
:::{}
```{r Number of Rows2, echo=F}
numericInput(inputId="NRows2",
             label="Waffle cols-plot2",
             value=2,
             min=1,
             max=30,
             step=1,
             width="120px")
```
:::
:::{}
```{r Number of Facet Rows, echo=F}
numericInput(inputId="FacetRows",
             label="No. facet rows",
             value=1,
             min=1,
             max=30,
             step=1,
             width="120px")
```
:::
:::{}
```{r Text Size, echo=F}
numericInput(inputId="TextSize",
             label="Text Size",
             value=20,
             min=1,
             max=30,
             step=1,
             width="80px")
```
:::
:::{}
```{r Text Wrap, echo=F}
  selectInput(inputId="TextWrap", 
             label="Wrap labels?",
              choices = c("Yes","No"),
              selected="No", 
              multiple = F, 
              width="100px")
```
:::
:::{}
```{r RmNoHaz, echo=F}
  selectInput(inputId="RmNoHaz", 
             label="Remove No Hazard?",
              choices = c("Yes","No"),
              selected="Yes", 
              multiple = F, 
              width="140px")
```
:::
:::{}
```{r LegPos,echo=F}
  selectInput(inputId="LegPos", 
              label="Legend position",
              choices = c("bottom", "right", "top", "left"),
              selected="bottom", 
              multiple = F, 
              width="120px")
```
:::
:::{}
```{r Facet spacing, echo=F}
numericInput(inputId="PanelSpace",
             label="Facet spacing",
             value=0,
             min=1,
             max=30,
             step=1,
             width="110px")
```
:::
:::{}
```{r Grid spacing, echo=F}
numericInput(inputId="GridSpace",
             label="Grid spacing",
             value=0.3,
             min=0,
             max=3,
             step=0.01,
             width="110px")
```
:::
:::{}
```{r Grid Cols, echo=F}
numericInput(inputId="GridCols",
             label="Grid columns",
             value=2,
             min=1,
             max=10,
             step=1,
             width="100px")
```
:::
:::{}
```{r Grid Rows, echo=F}

  numericInput(inputId="GridRows",
               label="Grid rows",
               value=3,
               min=1,
               max=10,
               step=1,
               width="100px")

```
:::
::::

:::: {style="display: flex;"}
::: {}
```{r Choose Plot,echo=F}
  selectInput(inputId="plot_choice", 
              label="Choose plot",
              choices = c("plot1","plot2"),
              selected="plot1", 
              multiple = F, 
              width="120px")
```
:::
:::{}
```{r Choose Palette,echo=F}
  selectInput(inputId="Palette", 
              label="Palette",
              choices = Palettes[,sort(Palette)],
              selected="turbo", 
              multiple = F, 
              width="150px")

HazardPalette<-reactive({PalFun(PalName=input$Palette,
                      N=nrow(HazTab),
                      Names=HazTab$Hazard)
})
```
:::
:::{}
```{r Plot background colour picker, echo =F}
  colourInput(inputId="Background",
              label="Background colour",
              value="white")
```
:::
:::{}
```{r Plot grid colour picker, echo =F}
  colourInput(inputId="GridCol",
              label="Grid colour",
              value="white")
```
:::
:::{}
```{r Plot no hazard colour picker, echo =F}
  colourInput(inputId="NoHazardCol",
              label="No hazard colour",
              value="grey50")
```
:::
::::

:::: {style="display: flex;"}
::: {}
```{r BigP - Adjust Plot Height, echo=F}
numericInput(inputId="Plot.Height",
             label="Adjust plot height",
             value=0.3,
             min=0.1,
             max=3,
             step=0.05, 
             width="200px")
```
:::
:::{}
```{r Adjust Plot Width , echo=F}
numericInput(inputId="Plot.Width",
             label="Adjust plot width",
             value=1.2,
             min=0.1,
             max=3,
             step=0.1,
             width="200px")
```
:::
::::

```{r subset data & adjust units, echo=F}
square_val<-reactive({
  dat<-Data[Label %in% input$Crops.Lab]
  max_vop<-10^(nchar(dat[,max(VoP)])-2)
  dat[,VoP:=VoP/max_vop]
  scale_factor<-dat[,max(VoP,na.rm = T)/input$Scaler]
  round(scale_factor*max_vop/10^6,1)
})

square_val2<-reactive({
    if(is.null(input$Countries)){
    dat<-Data[Region %in% input$Regions & Country==""]
  }else{
    dat<-Data[Country %in% input$Countries]
  }
  ranks<-dat[,sort(unique(Rank))][1:input$Crop.N2]
  dat<-dat[Rank2 %in% ranks]
  max_vop<-10^(nchar(dat[,max(VoP)])-2)
  dat[,VoP:=VoP/max_vop]
  scale_factor<-dat[,max(VoP,na.rm = T)/input$Scaler]
  round(scale_factor*max_vop/10^6,1)
})

```

Plot 1: Waffle grid unit = `r reactive(square_val())` million IntD 2015. Plot 2: Waffle grid unit = `r reactive(square_val2())` million IntD 2015.

```{r create plot function, echo=F}
#https://rud.is/rpubs/building-waffle-charts.html 

Waffler<-function(data,
                  Crops.Lab,
                  Crop.N2,
                  Regions,
                  Countries,
                  Scaler,
                  NRows,
                  NRows2,
                  FacetRows,
                  TextSize,
                  HazardPalette,
                  LegPos,
                  PanelSpace,
                  TextWrap,
                  RmNoHaz,
                  Background,
                  NoHazardCol,
                  GridSpace,
                  GridCol){
  
  if(TextWrap=="Yes"){
    data[,Crops:=gsub("oil crops","oil-crops",Crops)]
    data[!grepl(" ",Crop),Crop:=paste0(Crop,"\n")]
    data[,Crop:=gsub(" ","\n",Crop)]
  }

  if(RmNoHaz=="Yes"){
    data<-data[Hazard!="No hazard"]
  }
  
   if(RmNoHaz=="No"){
    HazardPalette[names(HazardPalette)=="No Hazard"]<-NoHazardCol
  }
  
  # Create combined names
  data[, Combined := paste0(Admin, ":", Crop)]
  data[, Combined := factor(Combined, levels = data[, .(Total = sum(VoP)), by = Combined][order(-Total), Combined])]
  
  # Factorize hazard
  data[,Hazard:=factor(Hazard,levels=sort(unique(Hazard)))]

  # Data for plot 1
  data1<-data[Label %in% Crops.Lab]
  max_vop<-10^(nchar(data1[,max(VoP)])-2)
  data1[,VoP:=VoP/max_vop]
  scale_factor<-data1[,max(VoP,na.rm = T)/Scaler]
  data1[,VoP:=round(VoP/scale_factor,0)]
  MaxY<-data1[,list(Height=ceiling(sum(VoP)/NRows)),by=.(Region,Country,Crop)][,max(Height)]+1

  # Data for plot 2
  if(is.null(Countries)){
    data2<-data[Region %in% Regions & Country==""]
  }else{
    data2<-data[Country %in% Countries]
  }
  ranks<-data2[,sort(unique(Rank))][1:Crop.N2]
  data2<-data2[Rank2 %in% ranks]
  max_vop<-10^(nchar(data2[,max(VoP)])-2)
  data2[,VoP:=VoP/max_vop]
  scale_factor<-data2[,max(VoP,na.rm = T)/Scaler]
  data2[,VoP:=round(VoP/scale_factor,0)]

  # Plot 2
gg_theme <- theme(
  text = element_text(size = TextSize),
  plot.margin = margin(0, 0, 0, 0, unit = "cm"), # Remove plot margin
  panel.spacing = unit(0, "lines"), # No space between panels
  axis.ticks = element_blank(),
  axis.line = element_blank(),
  panel.background = element_rect(fill = Background),
  strip.background = element_blank(),
  strip.text.y.left = element_text(
    angle = 0,                # Horizontal strip labels
    hjust = 1,                # Align strip labels horizontally
    vjust = 0.5,              # Center vertically
    margin = margin(r = 0, l = 0, unit = "pt") # Remove strip margins
  ),
  axis.text = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank()
)

  g <- ggplot(data2, aes(fill = Hazard, values = VoP)) +
  waffle::geom_waffle(n_rows = NRows2, size = GridSpace, colour = GridCol, flip = FALSE) +
  scale_fill_manual(values = HazardPalette, drop = FALSE) +
  scale_x_continuous(expand = c(0.005,0))+
  scale_y_continuous(expand = c(0.02,0.02))+
  facet_grid(Combined ~ ., switch = "y") + # Use facet_grid with switched strips
  gg_theme

  # Plot 1
  gg_theme<-theme(text=element_text(size=TextSize),
          panel.spacing = unit(PanelSpace,"lines"),
          axis.ticks = element_blank(),
          axis.line = element_blank(),
          panel.background = element_rect(fill=Background),
          strip.background = element_blank(),
          strip.text = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")),
          plot.margin = margin(0, 0, 0, 0, unit = "cm"), 
          axis.text = element_blank(),
          axis.title = element_blank(),
          panel.grid = element_blank()
          )
  
  Plots<-lapply(data1[,sort(unique(Admin))],FUN=function(REG){
    
    Plot.Dat<-data1[Admin==REG]
    
    Plot.Dat[,Crop:=factor(Crop,levels = unique(Plot.Dat[,.(Crop,Rank)])[order(as.numeric(Rank)),Crop])]
  
  g<-ggplot(Plot.Dat,aes(fill = Hazard, values = VoP)) +
    expand_limits(x=c(0,0), y=c(0,0)) +
    coord_equal() +
    labs(fill = NULL, colour = NULL) +
    waffle::geom_waffle(n_rows = NRows, size = GridSpace, colour = GridCol, flip = TRUE)+
    gg_theme+
    scale_fill_manual(values=HazardPalette,drop=F)+
    facet_wrap(~Crop, nrow = FacetRows, strip.position = "bottom")+
    scale_y_continuous(limits=c(0,MaxY),expand = c(0,0))
  
  g

  })
  
  names(Plots)<-data[,unique(Region)]

  return(list(Plot1=Plots,Plot2=g))
}

```

```{r create plots,echo=F}
PlotData<-reactive({
  Waffler(data=copy(Data),
          Crops.Lab=input$Crops.Lab,
          Crop.N2=input$Crop.N2,
          Regions=input$Regions,
          Countries=input$Countries,
          Scaler=input$Scaler,
          NRows=input$NRows,
          NRows2=input$NRows2,
          FacetRows=input$FacetRows,
          TextSize=input$TextSize,
          HazardPalette=HazardPalette(),
          LegPos=input$LegPos,
          PanelSpace=input$PanelSpace,
          TextWrap=input$TextWrap,
          RmNoHaz=input$RmNoHaz,
          Background=input$Background,
          NoHazardCol=input$NoHazardCol,
          GridSpace=input$GridSpace,
          GridCol=input$GridCol)
})

```

```{r Plot Size Adjust Functions , echo=F}
Plot.Height <- function(){
  x<-  input$Plot.Height*400*length(PlotData()$Plot1)
  if(input$plot_choice=="plot2"){
  x<-x*2
  }
  return(x)
}

Plot.Width <- function(){
  input$Plot.Width*1200
}
```

```{r Plot waffles,echo=F}
renderPlot({
  if(input$plot_choice=="plot1"){
  ggpubr::ggarrange(plotlist=PlotData()$Plot1, 
                    ncol=input$GridCols,
                    nrow=input$GridRows, 
                    common.legend = TRUE, 
                    legend=input$LegPos)
  }else{
     PlotData()$Plot2
  }
  },height= Plot.Height,width=Plot.Width)
```


:::: {style="display: flex;"}
::: {}
```{r  Save Waffle Option, echo=F}
selectInput(inputId="Waffle.Save.Plot", 
            label="Enable Save?",
            choices = c("Yes","No"),
            selected="No",
            width="150px")   
```
:::
:::{}
```{r Waffle Save Width, echo=F}
numericInput(inputId="Waffle.Width",
             label="Plot save width (mm)", 
             value=180,
             min=30,
             max=300,
             step=10,
             width="200px")  
```         
:::
:::{}
```{r Waffle Save Height, echo=F}
numericInput(inputId="Waffle.Height",
             label="Plot save height (mm)", 
             value=180,
             min=30,
             max=300,
             step=10,
             width="220px")  
```   
:::
:::{}
```{r Waffle Scale Height, echo=F}
numericInput(inputId="Waffle.Scale",
             label="Plot scaling", 
             value=1.8,
             min=0.5,
             max=4,
             step=0.1,
             width="200px")  
``` 
:::
:::{}
```{r Waffle - Plot Filename, echo=F}
textInput(inputId="Waffle.Filename",
          label="Enter Waffle filename", 
          value="Waffle")

```
:::
::::
  
```{r Save Waffle, echo=F}
reactive({
  if(input$Waffle.Save.Plot=="Yes"){
    ggsave(filename = paste0(input$Waffle.Filename,".png"),
           plot =   ggpubr::ggarrange(plotlist=PlotData(), 
                    ncol=input$GridCols,
                    nrow=input$GridRows, 
                    common.legend = TRUE, 
                    legend=input$LegPos),
           path = PlotDir,
           width= input$Waffle.Width,
           height = input$Waffle.Height,
           units = "mm",
           scale = input$Waffle.Scale,
           dpi = 600,
           type = "cairo")
  }
})
```


#### Data used the waffle plot:
```{r Show Data,echo=F}
renderDT({
  datatable(Data[,!c("Admin","Label","Rank","Rank2")][,Unit:=paste("2015",input$Units)],
            caption="Plot data by crop x region x hazard",
            extensions = 'Buttons',
            filter = "top",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),c(10,25,50,"All"))))
  
})
```

### Hazard map
:::: {style="display: flex;"}
::: {}
```{r Adjust Map Height, echo=F}
numericInput(inputId="Map.Height",
             label="Adjust map height",
             value=1,
             min=0.1,
             max=3,
             step=0.1, 
             width="160px")
```
:::
:::{}
```{r Adjust Map Width , echo=F}
numericInput(inputId="Map.Width",
             label="Adjust map width",
             value=1,
             min=0.1,
             max=3,
             step=0.1,
             width="160px")
```
:::
:::{}
```{r Map border colour picker, echo =F}
  colourInput(inputId="MapBorder",
              label="Border colour",
              value="black")
```
:::
:::{}
```{r Border Width , echo=F}
numericInput(inputId="BorderWidth",
             label="Border width",
             value=0.2,
             min=0.1,
             max=2,
             step=0.1,
             width="120px")
```
:::
:::{}
```{r Map Text Size , echo=F}
numericInput(inputId="MapTextSize",
             label="Text size",
             value=16,
             min=1,
             max=30,
             step=1,
             width="120px")
```
:::
::::

```{r Create Hazard Map Function,echo=F}

WorldMapFun<-function(PalName,
                      Hazard,
                      cgiar_countries,
                      MapBorder,
                      BorderWidth,
                      TextSize,
                      HazTab){
  
HazardPalette<-PalFun(PalName=PalName,
                      N=nrow(HazTab),
                      Names=HazTab$ShortName)

Hazards_Plot<-data.table(as.data.frame(raster::crop(raster::mask(Hazard,cgiar_countries),cgiar_countries),xy=T))
setnames(Hazards_Plot,"hazard","Code")
Hazards_Plot<-merge(Hazards_Plot,HazTab[,list(Code,ShortName)],by="Code",all.x=T)
setnames(Hazards_Plot,"ShortName","Hazards")

world <- ggplot2::map_data("world")

Countries<-cgiar_countries$ADMIN
Countries[Countries=="The Bahamas"]<-"Bahamas"
Countries[Countries=="Republic of the Congo"]<-"Republic of Congo"
Countries[Countries=="Guinea Bissau"]<-"Guinea-Bissau"
Countries[Countries=="East Timor"]<-"Timor-Leste"
Countries[Countries=="Trinidad and Tobago"]<-"Trinidad"
Countries[Countries=="United Republic of Tanzania"]<-"Tanzania"
Countries[Countries=="Saint Vincent and the Grenadines"]<-"Saint Vincent"
Countries[Countries=="eSwatini"]<-"Swaziland"
Countries[Countries=="United States Virgin Islands"]<-"Virgin Islands"
Countries<-Countries[!Countries %in% c("Netherlands","France")]

world<-world[world$region %in% Countries,]

g<-ggplot() +
  geom_raster(data = Hazards_Plot,
              aes(x = x, y = y, fill = Hazards))+
  scale_fill_manual(values=HazardPalette, na.value="white")+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = MapBorder, 
    fill = NA, 
    size = BorderWidth
  )+
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        text = element_text(size=TextSize,face="bold"),
        legend.position = c(0.8,0.2))+
  guides(fill=guide_legend(ncol=2))

return(g)
}
```

```{r create plot,echo=F}
Map<-reactive({
  WorldMapFun(PalName=input$Palette,
              Hazard = Hazard,
              cgiar_countries = cgiar_countries,
              MapBorder=input$MapBorder,
              BorderWidth=input$BorderWidth,
              TextSize = input$MapTextSize,
              HazTab = HazTab)
  })
```


```{r Map Size Adjust Functions , echo=F}
Map.Height <- function(){
  input$Map.Height*442
}

Map.Width <- function(){
  input$Map.Width*1200
}
```


```{r Plot Hazard Map,echo=F}
renderPlot({Map()},height=Map.Height,width=Map.Width)
```


:::: {style="display: flex;"}
::: {}
```{r  Save Map, echo=F}
selectInput(inputId="Map.Save.Plot", 
            label="Enable Save?",
            choices = c("Yes","No"),
            selected="No",
            width="120px")   
```
:::
:::{}
```{r Map Save Width, echo=F}
numericInput(inputId="Map.Save.Width",
             label="Map save width (mm)", 
             value=180,
             min=30,
             max=300,
             step=10,
             width="170px")  
```         
:::
:::{}
```{r Map Save Height, echo=F}
numericInput(inputId="Map.Save.Height",
             label="Map save height (mm)", 
             value=round(180*0.37),
             min=30,
             max=300,
             step=10,
             width="200px")  
```   
:::
:::{}
```{r Map Scale Height, echo=F}
numericInput(inputId="Map.Scale",
             label="Text scaling", 
             value=1.5,
             min=0.5,
             max=4,
             step=0.1,
             width="100px")  
``` 
:::
:::{}
```{r Map - Plot Filename, echo=F}
textInput(inputId="Map.Filename",
          label="Enter map filename", 
          value="Map")

```
:::
::::
  
```{r Save map, echo=F}

reactive({
  if(input$Map.Save.Plot=="Yes"){
    ggsave(filename = paste0(input$Map.Filename,".png"),
           plot = Map(),
           path = PlotDir,
           width= input$Map.Save.Width,
           height = input$Map.Save.Height,
           units = "mm",
           scale = input$Map.Scale,
           dpi = 600,
           type = "cairo")
  }
})



```

### Country x Hazard Table
```{r extract country data,echo=F}
renderDT({
  datatable(EX,
            caption="Cropland Hazards by Country",
            extensions = 'Buttons',
            colnames = c('Country', 'Crop area (km2)', '% crop at risk', 'Rural pop (M)',   '% pop at risk','Pop at risk (M)',colnames(EX)[7:length(colnames(EX))]), 
            filter = "top",
            options = list(dom = 'Blfrtip',
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           lengthMenu = list(c(10,25,50,-1),c(10,25,50,"All"))))
  
})

```